Golf-Sport: Managing Operations \\ A Case Study in Optimization

### 2018-03-27 Paper.tex
Sectioned
Divided into sections, start reference page, fixed ampersand issues.  Paper runs and compiles correctly at this point.

\documentclass{article}
\title{Golf-Sport:  Managing Operations \\ A Case Study in Optimization}
\date{May 8, 2018}
\author{John D. Bulger and xxxxxx, Valparaiso University}
%Add in Matt
\begin{document}
	\pagenumbering{gobble}
	\maketitle
	\newpage
	\pagenumbering{arabic}
\section{Introduction}
Hello world
\end{document}

>>>>

\documentclass{article}
\title{Golf-Sport:  Managing Operations \\ A Case Study in Optimization}
\date{May 8, 2018}
\author{John D. Bulger \& xxxxxx, Valparaiso University}
%Add in Matt
\begin{document}
	\pagenumbering{gobble}
	\maketitle
	\newpage
	\pagenumbering{arabic}
\section{Introduction}
This problem examines a manufacturing optimization case........
\section{Description of Problem}
This is where we describe what the problem we are trying to solve is
\section{Background and Prior Work}
Here is a good spot to insertour necessary references.  We can evaluate solutions of similar problems
\section{Mathematical Formulation \& Model}
\subsection{Assumptions}
Here we add assumptions about 2 month not going concern, minimization of inventory, selling all of per 1 and using period 3 for carryover
\subsection{Variables}
List our variables and indices, maybe in a table if i can figure out how to do it
\subsection{Objective}
Here we put in our objective function and explain the goal behind it
\subsection{Constraints}
Here we list all constraints in with an explanation surrounding each
\subsection{Heuristics}
Just kidding, this problem is not big enough for any heuristics
\section{Implementation}
\subsection{Hardware \& Software}
Problem was solved using MATLAB R2017B  It was run on a computer.....
\subsection{Coding}
%Maybe insert a page of pseudocode here???????
Code
\subsection{Algorithm}
Run as an IP using optimproblem, which is essentially an interior points method of solution.  Will run an LP to examine solutions
\section{Solution}
Explain results, compare to linear relaxation of the problem
\par
maybe insert a section with a graph or chart to visualize production
\section{Further Analysis}
Conduct range sensitivity, examine extra problems in case study
\section{Conclusions \& Implications}
\subsection{Mathematical Approach}
Evaluate our approach, suggest changes in future.  EFFICIENCY
\subsection{Company Approach}
Discuss optimized solution, range sensitivity, business suggestions
	\newpage
	\pagenumbering{gobble}
	\begin{thebibliography}{9}
\bibitem{bulger88}

\end{thebibliography}
\end{document}
